\section{Conclusion}\label{sec:conclusion}

In this paper we presented an enhanced approach for calculating the
CRPD taking into account the selected preemption points resulting
in greater accuracy.  Using a more precise CRPD calculation, we also
presented an improved algorithm for selecting a limited number of
preemption points for each task subject to schedulability constraints.
Our improved preemption placement algorithm was demonstrated to
minimize the overall preemption cost, an important result in achieving
schedulability in real-time systems.  We highlighted the iterative nature
of considering schedulability constraints in our preemption point
placement algorithm and proposed an algorithm combining schedulability
analysis with limited preemption point placement.  This approach
effectively illustrates how the individual tasks non-preemption
region parameters $Q_i$ and the optimal selected preemption points will
eventually converge.  Furthermore, our enhanced algorithm was demonstrated to be
optimal in that if a feasible schedule is not found, then no feasible
schedule exists by any known method utilizing a static $Q_i$ value.  Our algorithm
was shown to run in quadratic time complexity.  Potential preemption points can be
defined automatically using Gaisler's compiler and simulator along with AbsInt's
a\textsuperscript{3} tool or defined manually by the programmer during design
and implementation. Our experiments demonstrated the effectiveness of
the enhanced CRPD calculation by illustrating the benefits using the
task set from the MRTC WCET benchmark suite~\cite{mrtc:01}.
We also demonstrated the benefits of our enhanced limited optimal preemption
point placement algorithm and its increased system schedulability as
compared to other algorithms.  While our task model is defined using a linear
sequence of basic blocks, it was deemed a highly suitable model to introduce
our revised methods for enhanced CRPD calculation and optimal limited
preemption point placement.  The need to subsume higher level programming constructs
being the prominent assumption of the linear basic block structure can potentially
diminish the utility of our approach if the non-preemptive execution time of any basic block
violates the constraint \begin{math}C_{i}^{NP}\end{math} \begin{math}>\end{math} \begin{math}Q_{i}\end{math}.
%To overcome this limitation in future work, we plan to relax the linear basic block structure assumption and
%address arbitrarily connected basic block structures.
In future work, we plan to 1) extend the techniques described here to set-associative caches,
2) perform a schedulability comparison of synthetic task set for various preemption models, and
3) remove the linear basic block restriction thereby permitting arbitrarily connected basic
block structures.
